### 2019-10-02 english-activity.Rmd
(jusque 29/09)

---
title: "My english activity log"
---

24/09/2019 : I read some articles for my presentation.

25/09/2019 :I read some articles for my presentation.

27/09/2019 :I read some articles for my presentation and I searched for some Youtube channels about science (especially Biology). I found : iBiology, Biomentors Classes Online, Beverly Biology, Vincent Racaniello, Alex Lee, Sea&amp;me - Marine Biology stuff with Maria.

29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.

From now on, you will use this article to include every single activity that you do in English in a chronological order (e.g. reading a book in English, watching TV shows and series in English, going to an English Evening in Mons, travelling to an English-speaking country, playing games in English such as the pretty exciting game LyricsTraining, etc.). You can even write a few lines about what you’ve watched/read/done and recommend certain things to your friends. The sky’s the limit! We value personal initiative and we will be happy to read whatever you have to offer.

### 2019-10-02 english-activity.Rmd
jusque 29/09

@@
 
-From now on, you will use this article to include every single activity that you do in English in a chronological order (e.g.
-reading a book in English, watching TV shows and series in English, going to an English Evening in Mons, travelling to an English-speaking country, playing games in English such as the pretty exciting game LyricsTraining, etc.).
-You can even write a few lines about what you’ve watched/read/done and recommend certain things to your friends.
-The sky’s the limit!
-We value personal initiative and we will be happy to read whatever you have to offer.
+.

### 2019-10-06 english-activity.Rmd
29/09
jusque 02/10
jusque 06/10

@@
 29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.
+I read the first chapter of "The Hobbit"
 
-.
+02/10/2019 : I read the wikipedia article about cockatiel for my Data Science homework.
+
+05/10/2019 : I read some articles for my presentation and I watched a video about diffusion (https://www.youtube.com/watch?v=jhszFBtBPoI)
+
+06/10/2019 : I read some articles for my presentation, I read the second chapter of "The Hobbit" and I watched a vide about cell cycle (https://www.youtube.com/watch?v=QVCjdNxJreE)

### 2019-10-07 _posts/2019-09-18-article-1/article-1.Rmd
éléphant retiré

---
title: "Article 1 : "
author:
  - name: Aurélie Pinchart
date: 09-18-2019
categories:
  - 
  - 
preview: image/
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

![]

## Vocabulary

| Words from the text | Synonym/explanation in English |
| ------------------- | ------------------------------ |
| E.g. To cope with   | To deal with                   |
|                     | Not too distant future         |

## Analysis table

|                              |                                                                     |
| ---------------------------- | ------------------------------------------------------------------- |
| Researchers                  | (insert names and, if possible, professions)                        |
| Published in?                | (insert date)                                                       |
| General topic?               |  (summarize the topic in one or two sentences)                      |
| Procedure/what was examined? | (Give some details about the topic, i.e. methodology/material/etc.) |
| Conclusions/discovery?       |  (what did the researchers conclude? Did they find something?)      |
| Remaining questions?         | (check if there are still interrogations at the end of the article) |

### 2019-10-07 _posts/2019-09-18-article-1/article-1.Rmd
photo enlevée

@@
   - 
-preview: image/
+preview: 
 output:

### 2019-10-08 _posts/2019-09-18-article-1/article-1.Rmd
éléphant retiré ?

@@
 categories:
-  - 
-  - 
+  - track
 preview: 

### 2019-10-11 _posts/2019-09-18-article-1/article-1.Rmd
article 1 (texte + vocab + analyse)

--- 2019-10-07 _posts/2019-09-18-article-1/article-1.Rmd
@@
 ---
-title: "Article 1 : "
+title: "Article 1 : Pathway found for treatment-resistant lung cancer"
 author:
   - name: Aurélie Pinchart
-date: 09-18-2019
+date: 10-11-2019
 categories:
-  - 
-  - 
+  - track
 preview: 
@@
 ```
+## Article
 
-![]
+A big way **chemotherapy** works is by **prompting** cancer cells to commit suicide, and scientists have found a pathway the most common lung cancer walks to avoid death.
+Scientists at the Medical College of Georgia and Georgia Cancer Center at Augusta University have found a first step appears to be lung cancer cells expressing high levels of the molecule TIMP-1, classically considered a tumor inhibitor but at high levels already associated with a poor **prognosis** for patients.
+TIMP-1 then turns up expression of the **immune system** modulator IL-6, which is already associated with resistance to cancer chemotherapy.
+Levels of both increase even further in the face of chemotherapy treatment, a **mainstay** for treatment of the common, non-small cell lung cancer they studied.
+Chemotherapy resistance is a big problem in this lung cancer type, particularly when the cancer **recurs** at which point it's also more aggressive, says Dr. Mumtaz Rojiani, cancer biologist.
+To see just how TIMP-1 contributes, Rojiani and her colleagues first explored whether TIMP-1 **enabled** cancer cells' **uncanny** ability to essentially **spit out** a chemotherapy drug.
+While they didn't see evidence of that phenomenon in their studies in human lung cancer cells, they did see an increased level of IL-6.
+IL-6 is a sugar-coated protein that can turn inflammation both up and down and actually has been shown to regulate TIMP-1 -- rather than vice versa -- in some cancers.
+But in lung cancer, at least, the scientists saw TIMP-1 take the lead in avoiding cell suicide, a natural process that should happen when cells become **dysfunctional**.
+"At least in lung cancer, we are showing that it is TIMP-1 that is controlling IL-6," says Mumtaz Rojiani, corresponding author of the study in the journal Cancers.
+"We have shown for the first time that if TIMP-1 goes up, IL-6 goes up and if TIMP-1 goes down, IL-6 decreases ...
+and we have shown it in multiple different ways," says Dr.
+Amyn Rojiani, **chair** of the MCG Department of Pathology and a study coauthor.
+Their work indicates levels of this destructive duo may be an even more valuable indicator of a patient's prognosis as well as an important new **target** for improving it.
+In their studies, they looked at both human non-small cell lung cancer cells and the same cells with TIMP-1 knocked out, then used two **frontline** chemotherapeutic agents, gemcitabine and cisplatin, and found IL-6 production went down and cell death went up in response to the drugs in the cells with TIMP-1 missing, says Mumtaz Rojiani.
+"We gave the two chemotherapy drugs and when we looked at the effect of those drugs we found that TIMP-1 was affecting **apoptosis** in cell lines and when we **knocked it down**, we found more apoptosis even in the presence of these drugs," says Mumtaz Rojiani.
+"So we know TIMP-1 is affecting apoptosis."
+When they added TIMP-1, they saw IL-6 go back up and cell survival increase, she says.
+In fact, when they gave more IL-6, cell death also was reduced, however just adding TIMP-1 also increased IL-6 and using **antibodies** to **neutralize** just TIMP-1 also reduced levels of IL-6.
+When they looked again at cancer cells that survived, they were even more treatment-resistant than the cells they came from and had higher levels of TIMP-1 and IL-6, Mumtaz Rojiani says.
+"You develop chemo-resistant clones that have higher levels than the original cancer cells," says Amyn Rojiani.
+To **ensure** the IL-6 was functional at this higher level, they looked **downstream** at the IL-6 signaling pathway, which includes STAT3, a regulator of gene activity.
+STAT3 is known **to be involved in** controlling cell growth and division, movement and apoptosis, all of which cancer uses.
+With high levels of IL-6, they watched STAT3 move into the cell nucleus, which means it was also activated.
+To see if this tumor-promoting **synergy** they identified in human lung cancer cell lines also occurred in patients, they turned to the Cancer Genome Atlas database, compiled by the National Cancer Institute, which includes samples and full genome sequencing from patients with a huge variety of **outcomes**, including chemotherapy resistance and death, says Dr.
+Wei Xiao, MCG postdoctoral fellow and the study's first author.
+They found that patients with non-small cell lung cancer who had both low TIMP-1 and IL-6 had higher survival rates and these two genes were commonly elevated together, Xiao says.
+Also, just IL-6 being elevated did not affect survival as much as just TIMP-1 being elevated.
+But they found patient survival was much worse when both were elevated rather than TIMP-1 alone.
+"The two-gene signature became very important," says Mumtaz Rojiani.
+Next steps include examining exactly how STAT3 is helping reduce apoptosis in this scenario.
+They already are wondering if there is some sort of **feedforward** mechanism that also means another thing active STAT3 does is activate even more TIMP-1.
+They also want to look at other cancers to see if the same chain of events also is set in motion, particularly in those where others have reported it's IL-6 driving TIMP-1.
+The order definitely matters because it helps define the function of downstream molecules, they say.
+Theirs is the first report of this relationship where TIMP-1 affects IL-6, which activates STAT3 in this most common lung cancer type.
+Multiple studies have reported that TIMP-1 is significantly elevated in lung cancer cells versus healthy lung cells.
+Theirs defines a role for elevated TIMP-1 in cancer cells developing resistance to chemotherapy, the scientists say.
+Cancer makes **heavy-handed** use of both MMPs, or matrix metalloproteinases, and their natural inhibitor TIMP-1.
+MMPs get **secreted** following injury to degrade **adjacent** **tissue** like collagen so **a myriad** of cells and factors can move in for repair.
+Particularly near the end of the repair process, levels of TIMP-1 increase to help keep the process from getting out of hand and healthy tissue from also getting destroyed, says Amyn Rojiani.
+Cancer takes advantage of MMPs to ensure it can grow at its main site and spread to others.
+If we don't have an injury -- or cancer -- we likely have very low levels of TIMP-1, the scientists say.
+Lung cancer is the leading cause of cancer death in both men and women, and the non-small cell type accounts for 80-85 percent of lung cancers, according to the American Cancer Society.
+The Georgia Cancer Coalition helped fund the research.
+
+Source : MEDICAL COLLEGE OF GEORGIA AT AUGUSTA UNIVERSITY.
+"PATHWAY FOUND FOR TREATMENT-RESISTANT LUNG CANCER." SCIENCEDAILY.
+SCIENCEDAILY, 23 SEPTEMBER 2019.
+<WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.
+
+Word count : 1055
 
@@
 
-| Words from the text | Synonym/explanation in English |
-| ------------------- | ------------------------------ |
-| E.g. To cope with   | To deal with                   |
-|                     | Not too distant future         |
+I used https://www.wordreference.com/, https://www.lexico.com/ and https://dictionary.cambridge.org to fill in this table.
+
+| Vocabulary                      | Pronunciation     | Definition / synonym                                                               | French translation             |
+| ------------------------------- | ----------------- | ---------------------------------------------------------------------------------- | ------------------------------ |
+| The chemotherapy                | [ˌkiːməʊˈθɛrəpi]  | drug treatment of cancer                                                           | chimiothérapie                 |
+| To prompt sb. / sth. to do sth. | [ˈprɒmpt]         | to encourage to do sht.                                                            | pousser qqn /qqch à faire qqch |
+| The prognosis                   | [prɒgˈnəʊsɪs]     | doctor's judgement of your disease                                                 | pronostic                      |
+| The immune system               | [ɪˈmjuːn ˈsɪstəm] | biological defense mechanisms                                                      | système immunitaire            |
+| The mainstay                    | [ˈmeɪnsteɪ]       | most important part of something, providingsupport for everything else             | un pilier, un élément de base  |
+| To recur                        | [rɪˈk3ːr]         | happen again                                                                       | se reproduire, réapparaître    |
+| To enable                       | [ɪnˈeɪbəl]        | make possible                                                                      | permettre                      |
+| Uncanny                         | [ˌʌnˈkæni]        | strange                                                                            | étrange, troublant             |
+| To spit out (chemotherapy)      | [ˈspɪt ˈaʊt]      | reject the treatment                                                               | rejeter, résister à            |
+| Dysfunctional                   |  [dɪsˈfʌŋkʃənəl]  | that does not work good                                                            | dysfonctionnel, anormal        |
+| The chair                       | [ˈtʃɛər]          | person in charge if of meeting, official group or organization                     | le président (d'un comité)     |
+| To target                       | [ˈtɑːrgɪt]        | aim an attack                                                                      | cibler                         |
+|  frontline                      | [ˌfrʌntˈlaɪn]     | at the battlefront                                                                 | en première ligne              |
+| The apoptosis                   | [ˌæpəpˈtoʊsəs]    | natural cell death                                                                 | apoptose                       |
+| To knock sth. down              |  [ˈnɒk ˈdaʊn]     | destroy                                                                            | détruire                       |
+| The antibody                    | [ˈæntibɒdi]       | blood protein that recognize pathogens                                             | anticoprs                      |
+| To neutralize                   | [ˈnjuːtrəlaɪz]    | produce an effect that removes the effect of something else                        | neutraliser                    |
+| To ensure sth.                  | [ɪnˈʃʊər]         | make sure that                                                                     | s'assurer que                  |
+| Downstream                      | [ˌdaʊnˈstriːm]    |  happening later in a process or series of events                                  | en aval                        |
+|  involved in                    | [ɪnˈvɒlvd ˈɪn]    | taking part in an activity                                                         | impliqué dans                  |
+| The synergy                     | [ˈsɪnərdʒi]       | combined effect                                                                    | synergie                       |
+| The outcome                     | [ˈaʊtkʌm]         | result                                                                             | résultat                       |
+| Feedforward                     | [ˈfiːdfɔːwəd]     | predicting                                                                         | prédictif                      |
+| Heavy-handed                    | [ˌhɛviˈhændɪd]    | severe                                                                             | brutal, sévère                 |
+| To secrete                      | [sɪˈkriːt]        | emit                                                                               | sécréter                       |
+| Adjacent                        | [əˈdʒeɪsənt]      | that is beside                                                                     | adjacent                       |
+| The tissue                      |  [ˈtɪsjuː]        | a group of connected cells  that are similar to each other, have the same purpose  | tissu                          |
+| A myriad of                     | [ˈmɪriəd]         | a large number                                                                     | une myriade de                 |
 
@@
 |                             |                                                                                                                                                                                                                                                                                                                                                                           |
-| ---------------------------- | ------------------------------------------------------------------- |
-| Researchers                  | (insert names and, if possible, professions)                        |
-| Published in?                | (insert date)                                                       |
-| General topic?               |  (summarize the topic in one or two sentences)                      |
-| Procedure/what was examined? | (Give some details about the topic, i.e. methodology/material/etc.) |
-| Conclusions/discovery?       |  (what did the researchers conclude? Did they find something?)      |
-| Remaining questions?         | (check if there are still interrogations at the end of the article) |
+| --------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
+| Researchers                 | Medical College of Georgia at Augusta University (lead authors : Dr.
+Wei Xiao, Dr.
+Mumtaz Rojiani, Dr.
+Amyn Rojiani)                                                                                                                                                                                                                                                      |
+| Published in                | ScienceDaily, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
+| General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |
+| Procedure/what was examined | goal was to evidence link between TIMP-1 and resistance to chemotherapy + they used two drugs to destroy TIMP-1, then also destroy it by antibodies + added TIMP-1 to see the effect, then added IL-6  + STAT3 : regulator of gene activity (cell growth,division,  movement, apoptosis)                                                                                  |
+| Conclusions/discovery       | high rate of TIMP-1 increases rate of IL-6 which make cells avoid apoptosis + low rate of TIMP-1 => lower rate of IL-6 => more apoptosis of cancerous cells => higher survival rate for patients + adding IL-6 has no real effect on apoptosis + remaining cancerous cells are more resistant + high level of IL-6 => STAT3 moves to nucleus => helps to reduce apoptosis |
+| Remaining questions         | Does STAT3 activate more TIMP-1 production ?
+|
+
+## Source de l'article
+
+MEDICAL COLLEGE OF GEORGIA AT AUGUSTA UNIVERSITY.
+"PATHWAY FOUND FOR TREATMENT-RESISTANT LUNG CANCER." SCIENCEDAILY.
+SCIENCEDAILY, 23 SEPTEMBER 2019.
+<WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.

### 2019-10-13 english-activity.Rmd
jusqu'au 13/10/209

--- 2019-10-02 english-activity.Rmd
@@
 29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.
+I read the first chapter of "The Hobbit".
 
-.
+02/10/2019 : I read the wikipedia article about cockatiel for my Data Science homework.
+
+05/10/2019 : I read some articles for my presentation and I watched a video about diffusion (https://www.youtube.com/watch?v=jhszFBtBPoI).
+
+06/10/2019 : I read some articles for my presentation, I read the second chapter of "The Hobbit" and I watched a vide about cell cycle (https://www.youtube.com/watch?v=QVCjdNxJreE).
+
+09/10/2019 : I read an article for my presentation.
+
+10/10/2019 : I watched a video about the respiratory system (https://www.youtube.com/watch?v=2guHOnEt0e8).
+
+11/10/2019 : I worked on my first article for my portfolio.
+
+12/10/2019 : I read some articles for my presentation.
+
+13/10/2019 : I worked on my presentation and I read the third chapter of "The Hobbit".

### 2019-10-20 _posts/2019-10-18-article-2/article-2.Rmd
jusqu'au 20/10/2019

---
title: "article-2"
description: |
  A short description of the post.
author:
  - name: Aurélie Pinchart
    url: {}
date: 10-18-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

### 2019-10-20 english-activity.Rmd
jusqu'au 20/10/2019

@@
 13/10/2019 : I worked on my presentation and I read the third chapter of "The Hobbit".
+
+14/10/2019 : I read some articles for my presentation.
+
+15/10/2019 : I read some articles for my presentation and I watched a documentary about coral bleaching https://www.youtube.com/watch?v=5cr8S5tTiz4.
+
+16/10/2019 : I read some articles for my presentation.
+
+17/10/2019 : I watched a video about the types of natural selection https://www.youtube.com/watch?v=DBPGLythma0.
+
+19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU.
+
+20/10/2019 : I watched a video about resting potential but it was said the opposite of what we were taught in class (so I don't put the link).

### 2019-10-21 _posts/2019-09-18-article-1/article-1.Rmd
test pour le mettre en ligne
suppression de l'article dans le texte

--- 2019-10-07 _posts/2019-09-18-article-1/article-1.Rmd
@@
 
-![]
+Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.
 
@@
 |                             |                                                                                                                                                                                                                                                                                                                                                                           |
-| ---------------------------- | ------------------------------------------------------------------- |
-| Researchers                  | (insert names and, if possible, professions)                        |
-| Published in?                | (insert date)                                                       |
-| General topic?               |  (summarize the topic in one or two sentences)                      |
-| Procedure/what was examined? | (Give some details about the topic, i.e. methodology/material/etc.) |
-| Conclusions/discovery?       |  (what did the researchers conclude? Did they find something?)      |
-| Remaining questions?         | (check if there are still interrogations at the end of the article) |
+| --------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
+| Researchers                 | Medical College of Georgia at Augusta University (lead authors : Dr.
+Wei Xiao, Dr.
+Mumtaz Rojiani, Dr.
+Amyn Rojiani)                                                                                                                                                                                                                                                      |
+| Published in                | ScienceDaily, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
+| General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |
+| Procedure/what was examined | goal was to evidence link between TIMP-1 and resistance to chemotherapy + they used two drugs to destroy TIMP-1, then also destroy it by antibodies + added TIMP-1 to see the effect, then added IL-6  + STAT3 : regulator of gene activity (cell growth,division,  movement, apoptosis)                                                                                  |
+| Conclusions/discovery       | high rate of TIMP-1 increases rate of IL-6 which make cells avoid apoptosis + low rate of TIMP-1 => lower rate of IL-6 => more apoptosis of cancerous cells => higher survival rate for patients + adding IL-6 has no real effect on apoptosis + remaining cancerous cells are more resistant + high level of IL-6 => STAT3 moves to nucleus => helps to reduce apoptosis |
+| Remaining questions         | Does STAT3 activate more TIMP-1 production ?
+|

### 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
ajout du lien vers le pdf
date article + nbre de mots

@@
 
-Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.
+Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>, published on 23 September 2019
+
+Article with highlighted words : https://github.com/aureliepinchart/aurelie-pinchart-blog/blob/master/pdf/article_1.pdf
+
+Word count : 1055
 

### 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
categories

@@
 categories:
-  - track
+  - apoptosis
+  - TMP-1
+  -IL-6
 preview: 

### 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
categories (2eme essai)

--- 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
@@
 categories:
-  - track
+  - apoptosis
+  - TMP-1
+  - IL-6
 preview: 

### 2019-10-27 english-activity.Rmd
(jusqu'au 20/10/2019)
jusqu'au 27/10/2019

@@
 
-19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU.
+19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU. I also read the fouth chapter of "The Hobbit".
 
 20/10/2019 : I watched a video about resting potential but it was said the opposite of what we were taught in class (so I don't put the link).
+
+22/10/2019 : I watched a video about predation https://www.youtube.com/watch?v=6jXwEOit5vM.
+
+24/10/2019 : I watched a video about genetic drift https://www.youtube.com/watch?v=W0TM4LQmoZY and a video about natural selection https://www.youtube.com/watch?v=7VM9YxmULuo.
+
+26/10/2019 : I watched a video about the loss of biodiversity https://www.youtube.com/watch?v=vCkDxD0DV0Q and I read the fifth chapter of "T he Hobbit".
+
+27/10/2019 : I watched a video about the protein structure and folding https://www.youtube.com/watch?v=hok2hyED9go.

### 2019-11-01 _posts/2019-09-18-article-1/article-1.Rmd
jusqu'au 27/10/2019
article 2

--- 2019-10-23 _posts/2019-09-18-article-1/article-1.Rmd
@@
 categories:
-  - track
+  - apoptosis
+  - TMP-1 & IL-6
 preview: 
@@
 
-Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>, published on 23 September 2019
+## Source of the article
+
+ <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>, published on 23 September 2019
 

### 2019-11-01 _posts/2019-10-18-article-2/article-2.Rmd
article 2

@@
 ---
-title: "article-2"
-description: |
-  A short description of the post.
+title: "Article 2 : Antioxidants may encourage the spread of lung cancer rather than prevent it"
 author:
   - name: Aurélie Pinchart
-    url: {}
-date: 10-18-2019
+date: 11-01-2019
+categories:
+  - antioxidants
+  - oxidatice stress
+preview: article-2_image/antioxidants.jpg
 output:
@@
 ```
+![](../2019-10-18-article-2/article-2_image/antioxidants.jpg)
 
-Distill is a publication format for scientific and technical writing, native to the web.
+## Source of the article
 
-Learn more about using Distill at <https://rstudio.github.io/distill>.
+Nicoletta Lanese.
+« Antioxidants may encourage the spread of lung cancer rather than prevent it ».
+Science News.
+June 27, 2019.
+<https://www.sciencenews.org/article/antioxidants-lung-cancer-spread-prevent>
+
+Word count : 668
+
+## Vocabulary
+
+I used https://www.wordreference.com/, https://en.wiktionary.org/ and https://dictionary.cambridge.org to fill in this table.
+
+| Vocabulary                    | Pronunciation       | Definition / synonym                                                                                               | French translation         |
+| ----------------------------- | ------------------- | ------------------------------------------------------------------------------------------------------------------ | -------------------------- |
+| mechanism                     | [ˈmɛkənɪzəm]        | the way something works                                                                                            | mécanisme                  |
+| metastasis                    | [mɪˈtæstəsɪs]       | the spread of cancer                                                                                               | métastase                  |
+| to thwart                     | [ˈθwɔːrt]           | stop sth.
+from happening                                                                                           | contrecarrer               |
+| Antioxidant                   | [ˌæntiˈɒksɪdənt]    | type of nutrients that protect cells from free-radicals                                                            | antioxydant                |
+| to tout                       | [ˈtaʊt]             | tell that sth.
+is good for you (in ads for example)                                                                | promouvoir                 |
+| to spur (sth./sb.
+to do sth.) | [ˈsp3ːr]            | encourage                                                                                                          | inciter, pousser à         |
+| to figure out                 | [ˈfɪgər ˈaʊt]       | understand                                                                                                         | comprendre                 |
+| dietary                       | [ˈdaɪətəri]         | related to diet                                                                                                    | alimentaire                |
+| invade                        | [ɪnˈveɪd]           | enter a place in large number (when unwanted)                                                                      | envahir                    |
+| safeguard (against)           | [ˈseɪfgɑːrd]        | protect (from)                                                                                                     | protéger                   |
+| tumor                         | [ˈtu·mər]           | abnormal growth of cells                                                                                           | tumeur                     |
+| to pile up                    | [ˈpaɪl ˈʌp]         | accumulate                                                                                                         | s'accumuler                |
+| glucose                       | [ˈgluːkəʊz]         | type of sugar                                                                                                      | glucose                    |
+| to fuel                       | [ˈfjuːəl]           | to give energy                                                                                                     | alimenter                  |
+| to claim (lives)              | [ˈkleɪm]            | to cause death                                                                                                     | causer la mort             |
+| colon                         | [ˈkəʊlən]           | large intestin                                                                                                     | colon                      |
+| breast                        | [ˈbrɛst]            | woman's organ that produces milk                                                                                   | le sein                    |
+| prostate                      | [ˈprɒsteɪt]         | male urinary gland                                                                                                 | prostate                   |
+| connected the dots            | [kəˈnɛkt ˈðə ˈdɒts] | understand                                                                                                         | comprendre                 |
+| free radical                  | [ˈfriː ˈrædɪkəl]    | very reactive molecule (because of an extra electron)                                                              | radical libre              |
+| metabolism                    | [mɪˈtæbəlɪzəm]      | all the reactions inside the cell                                                                                  | métabolisme                |
+| tweak                         | [ˈtwiːk]            | small change                                                                                                       | petite modification        |
+| suite                         | [ˈswiːt]            | group                                                                                                              |  ensemble                  |
+| fervent                       | [ˈf3ːrvənt]         | ardent                                                                                                             | fervent, ardent            |
+| perk                          | [ˈp3ːrk]            | advantage                                                                                                          | avantage                   |
+| amok                          | [əˈmɒk]             | wild                                                                                                               | déchaîné                   |
+| to run amok                   | [ˈrʌn əˈmɒk]        | get out of control                                                                                                 | devenir incontrôlable      |
+| free-floating                 | [ˌfriːfləʊtɪŋ]      | not attached to anything                                                                                           | flottant                   |
+| heme                          | [hiːm]              | prosthetic group of hemoprotein, containing iron                                                                   | hème                       |
+| pigment                       | [ˈpɪgmənt]          | molecule that gives colour to sth.
+| pigment                    |
+| employ                        | [ɪmˈplɔɪ]           | use                                                                                                                | employer, utiliser         |
+| enzyme                        | [ˈɛnzaɪm]           | protein that speeds up a specific biological reaction                                                              | enzyme                     |
+| to hijack                     | [ˈhaɪdʒæk]          | to take control of sth.
+| détourner                  |
+| degrade                       | [dɪˈgreɪd]          | to break into more simple molecules                                                                                | dégrader                   |
+| metastasized                  | [mɪˈtæstəˌsaɪz]     | spread                                                                                                             | métatstaser                |
+| to mimic                      | [ˈmɪmɪk]            | imitating                                                                                                          | imiter                     |
+| uptake                        | [ˈʌpteɪk]           | absorption of nutrients in cells                                                                                   | assimilation               |
+| to unearth                    | [ˌʌnˈ3ːrθ]          | discover, find                                                                                                     | trouver, découvrir         |
+| to exacerbate                 | [ɪgˈzæsərbeɪt]      | intensify                                                                                                          | exacerber                  |
+| to undermine                  | [ˌʌndərˈmaɪn]       | make weaker                                                                                                        | affaiblir                  |
+| glycolysis                    | [ɡlaɪˈkɒlɪsɪs]      | biochemical process that cleaves one molecule of glucose and produces two molecules of pyruvate and energy         | glycolyse                  |
+| to guzzle                     | [ˈgʌzəl]            | eat a lot                                                                                                          | engloutir, manger beaucoup |
+| to inherit                    | [ɪnˈhɛrɪt]          | (in this case) get some characteristic from your ancestors (genes)                                                 | hériter (de)               |
+| porphyria                     | [pɔːˈfɪrɪə]         | disease caused by a too big amount of porphyrins (enzymes, found in hemoglobin for example) in the blood and urine | porphyrie                  |
+| potent                        | [ˈpəʊtənt]          | strong                                                                                                             | puissant, fort             |
+
+## Analysis
+
+|                               |                                                                                                                                                                                                                                                                                                                                                                                                             |
+| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
+| Researchers                   | (two studies) 1) Michele Pagano (New York University School of Medicine) 2) Martin Bergö (Karolinska Institutet in Stockholm)                                                                                                                                                                                                                                                                               |
+| General topic                 | the bad effect of antioxidants when you have lung caner                                                                                                                                                                                                                                                                                                                                                     |
+| Published in                  | Science News, 27 June 2019                                                                                                                                                                                                                                                                                                                                                                                  |
+| Procedure / what was examined |  experiments on mice and humans  1) antioxidant- producing genes + effect of antioxidants 2) antioxidant // dietary supplement                                                                                                                                                                                                                                                                              |
+| Conclusion / discovery        | 1) antioxidants protect cancerous cells + help to accumulate protein Bach1 => more glycolysis => encourage metastasis + cancerous cells have mutations in genes producing antioxidants => higher production => production of Nrf2 => highe rate og Ho1 => protection from free radicals 2) higher rates of Bach1 protein + Bach1 activate genes that accelerate glucose uptake and glycolysis => metastases |
+| Remaining questions           | finding drugs to inhibit Ho1, Bach1 and decrease glycolysis + giving inhibitors used to treat porphyrias to patients affected by lung cancer + Why some lung cancer metastasizes and other don't ?
++ Do these proteins also play a role in other cancers ?
+|

### 2019-11-01 _posts/2019-10-18-article-2/article-2.Rmd
correction faute

@@
   - antioxidants
-  - oxidatice stress
+  - oxidative stress
 preview: article-2_image/antioxidants.jpg

### 2019-11-03 _posts/2019-11-02-article-3/article-3.Rmd
jusqu'au 03/11/2019

---
title: "article-3"
description: |
  A short description of the post.
author:
  - name: Aurélie Pinchart
    url: {}
date: 11-02-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

### 2019-11-03 english-activity.Rmd
jusqu'au 03/11/2019

@@
 27/10/2019 : I watched a video about the protein structure and folding https://www.youtube.com/watch?v=hok2hyED9go.
+
+29/10/2019 : I watched a video about mutations https://www.youtube.com/watch?v=vl6Vlf2thvI.
+
+01/11/2019 : I watched a video about microscope drawings https://www.youtube.com/watch?v=NLKZ95aHqE4.
+
+02/11/2019 : I watched a video about ethology https://www.youtube.com/watch?v=BvLihzeQzGk.
+
+03/11/2019 : I watched a video about stress management https://www.youtube.com/watch?v=2vhIGYKW4gY and I read the sixth chapter of "The Hobbit".

### 2019-11-10 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
chgmt my english activity log
ajout image
jusqu'au 10/11/2019

--- 2019-11-03 english-activity.Rmd
@@
 ---
-title: "My english activity log"
+title: "My English activity log"
+
+author:
+  - name: Aurélie Pinchart
+date: 11-04-2019
+preview: english.jpg
+output:
+  distill::distill_article:
+    self_contained: false
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
+```
 
@@
 03/11/2019 : I watched a video about stress management https://www.youtube.com/watch?v=2vhIGYKW4gY and I read the sixth chapter of "The Hobbit".
+
+05/11/2019 : I watched a video about ethology (the second part) https://www.youtube.com/watch?v=jEZIUVU0BCU.
+
+07/11/2019 : I watched  the last part of the video about ethology https://www.youtube.com/watch?v=bspxe_-ilC4.
+
+09/11/2019 : I watched a video about enzymes https://www.youtube.com/watch?v=6Acx6b3Hzsk 
+10/11/2019 : I watched a video about germination https://www.youtube.com/watch?v=cmzhvl5kOc0 and I read the seventh chapter of "The Hobbit".

### 2019-11-15 _posts/2019-11-02-article-3/article-3.Rmd
article 3

@@
 ---
-title: "article-3"
-description: |
-  A short description of the post.
+title: "Article 3 : New blood test trialled on 12,000 Scots catches lung cancer early"
+
 author:
   - name: Aurélie Pinchart
-    url: {}
-date: 11-02-2019
+date: 11-15-2019
+categories:
+  - blood test
+preview: lung_image.jpg
 output:
@@
 
-Distill is a publication format for scientific and technical writing, native to the web.
+![](lung_image.jpg)
 
-Learn more about using Distill at <https://rstudio.github.io/distill>.
+## Soruce of the article
+
+https://www.bbc.com/news/uk-scotland-49638208 published on 10 September 2019.
+
+Word count : 551
+
+## Vocabulary
+
+I used https://www.wordreference.com/, https://www.dictionary.cambridge.org/, https://www.lexico.com/ to fill in this table.
+
+| Vocabulary       | Pronunciation       | Definition / synonym                                                            | French translation              |
+| ---------------- | ------------------- | ------------------------------------------------------------------------------- | ------------------------------- |
+| blood test       | [ˈblʌd ˈtɛst]       | analysis of a blood sample                                                      | analyse sanguine                |
+| symptom          | [ˈsɪmptəm]          | sign of a disease                                                               | symptôme                        |
+|  diagnose (with) | [ˈdaɪəgnəʊz]        | find the illness you have                                                       | diagnostiquer                   |
+| undiagnosed      | [ʌnˈdʌɪəɡnəʊzd]     | not diagnosed yet                                                               | non diagnostiqué                |
+| trial            | [ˈtraɪəl]           | clinical testing                                                                | essai, test                     |
+| clinical         | [ˈklɪnɪkəl]         | refering to medical work related to the examination and treatment of ill people | clinique                        |
+| recruit          | [rɪˈkruːt]          | seek for employment                                                             | recruter                        |
+| former           | [ˈfɔːrmər]          | ~ that used to be                                                               | ex, ancien                      |
+| Meanwhile        | [ˈmiːnhwaɪl]        | at the same time                                                                | pendant ce temps-là             |
+| landmark         | [ˈlændmɑːrk]        | important                                                                       | important, majeur, capital      |
+| significant      | [sɪgˈnɪfɪkənt]      | important                                                                       | significatif, important         |
+| surgery          | [ˈs3ːrdʒəri]        | surgical intervention,  operation                                               | opération chirurgicale          |
+| prospect (for)   | [prəˈspɛkt]         | seek , look for                                                                 | prospecter, chercher            |
+|  roll out        | [ˈrəʊl ˈaʊt]        | introduce sth new to public                                                     | lancer                          |
+| aim              | [ˈeɪm]              | objective, purpose                                                              | but, objectif                   |
+| liver            | [ˈlɪvər]            | an organ that cleans the blood and produces bile                                | foie                            |
+| ovarian          | [əʊˈvɛəriən]        | related to the ovaries                                                          | ovarien                         |
+| in pursuit of    | [ˈɪn pərˈsjuːt ˈɒv] | seeking                                                                         | à la recherche de, en quête de  |
+| oncology         | [ɒŋˈkɒlədʒɪ]        | study and treatment of cancer                                                   | oncologie                       |
+
+## Analysis
+
+|                               |                                                                                                                                                                                                 |
+| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
+| Researchers                   | Prof Frank Sullivan                                                                                                                                                                             |
+| General topic                 | detection of lung cancer                                                                                                                                                                        |
+| Published in                  | BBC, 10 September 2019 (presented a few days earlier in World Conference of Lung cancer in Barcelona)                                                                                           |
+| Procedure / what was examined | trial on more than 12,000 people who were at risk (smokers and former smokers, between 50 and 75 years old) : blood test + CT scans (= computed tomography scans) + detection of autoantibodies |
+| Conclusion / discovery        | detecting lung cancer at an early stage is possible : lower death rates and lower cost of treatment                                                                                             |
+| Remaining questions           |                                                                                                                                                                                                 |

### 2019-11-17 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 17/11/2019

@@
 10/11/2019 : I watched a video about germination https://www.youtube.com/watch?v=cmzhvl5kOc0 and I read the seventh chapter of "The Hobbit".
+
+13/11/2019 : I watched a video about CRISPR https://www.youtube.com/watch?v=MnYppmstxIs.
+
+15/11/2019 : I watched a video about ATP https://www.youtube.com/watch?v=23ZzI6WZS28.
+
+16/11/2019 : I watched a video about bacteria https://www.youtube.com/watch?v=ORB866QSGv8.
+
+17/11/2019 : I watched a video about autotrophs and heterotrophs https://www.youtube.com/watch?v=f8G7IulYxiA and I read the eighth of "The Hobbit".

### 2019-11-24 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 24/11/2019

@@
   - name: Aurélie Pinchart
-date: 11-04-2019
+date: 11-24-2019
 preview: english.jpg
@@
 17/11/2019 : I watched a video about autotrophs and heterotrophs https://www.youtube.com/watch?v=f8G7IulYxiA and I read the eighth of "The Hobbit".
+
+20/11/2019 : I watched a video about DNA and RNA https://www.youtube.com/watch?v=JQByjprj_mA.
+
+21/11/2019 : I watched a video about skin https://www.youtube.com/watch?v=b9Fim9kKVLs.
+
+23/11/2019 : I watched a video about reflex arc https://www.youtube.com/watch?v=SMcF01utk3Y.
+
+24/11/2019 : I watched a video about signal transduction pathways https://www.youtube.com/watch?v=236d5LDUFSs and I read the ninth chapter of "The Hobbit".

### 2019-11-30 _posts/2019-11-29-article-4/article-4.Rmd
article 4

---
title: "Article 4 : Two therapeutic targets identified for deadly lung cancer"
author:
  - name: Aurélie Pinchart
date: 11-29-2019
categories:
  - LKB1
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Source of the article

Salk Institute. "Two therapeutic targets identified for deadly lung cancer: Scientists discover a pair of enzymes that drive non-small-cell lung cancer by promoting inflammation." ScienceDaily. ScienceDaily, 26 July 2019. <www.sciencedaily.com/releases/2019/07/190726153155.htm>.

## Vocabulary

I used https://www.lexico.com/, https://dictionary.cambridge.org/, https://www.wordreference.com/ to fill in this table.

| Vocabulary                               | Pronunciation                               | Definition / synonym                                                        | French translation                          |
| ---------------------------------------- | ------------------------------------------- | --------------------------------------------------------------------------- | ------------------------------------------- |
| majority                                 | [məˈdʒɒrɪti]                                | over 50%                                                                    | majorité                                    |
| term                                     | [ˈt3ːrm]                                    | give a name                                                                 | appeler                                     |
| carcinomas                               | [ˌkɑːsɪˈnəʊmə]                              | cancerous tumor                                                             | carcinome                                   |
| mutated                                  | [mjuːˈteɪt]                                 | change (genes)                                                              | muter                                       |
| hopefully                                | [ˈhəʊpfʊli]                                 | with hope                                                                   | avec espoir                                 |
| function                                 | [ˈfʌŋkʃən]                                  | work properly                                                               | fonctionner                                 |
| suppressor                               | [səˈprɛsər]                                 | sth. preventing sth. else to happen                                         | limitateur                                  |
| relay                                    | [ˈriːleɪ]                                   | race between several teams in which each person performs a part of the race | course de relais                            |
| baton                                    | [ˈbætɒn]                                    | the stick that you give to the next person in a relay                       | (bâton) témoin                              |
| kinase                                   | /ˈkʌɪneɪz/                                  | enzyme that adds phosphate groups                                           | kinase                                      |
| suppressive                              | [səˈpresɪv]                                 | stopping / reducing sth.                                                    | suppresseur                                 |
| unclear                                  | [ʌnˈklɪər]                                  | unclear                                                                     | pas clair                                   |
| disrupt                                  | [dɪsˈrʌpt]                                  | cause disorder                                                              | perturber, bouleverser                      |
| whodunnit                                | [huːˈdʌnɪt]                                 | murder story                                                                | roman policier                              |
| case                                     | [ˈkeɪs]                                     | question                                                                    | question                                    |
| point                                    | [ˈpɔɪnt]                                    | indicate                                                                    | indiquer                                    |
| backup                                   | [ˈbækʌp]                                    | the person who will play if the usual player is not available               | (joueur) de secours, de réserve             |
| intrigued                                | [ɪnˈtriːg]                                  | interest                                                                    | intriguer                                   |
| In a related  vein                       | [ˈɪn ə rɪˈleɪtɪd ˈveɪn]                     | regarding the same object                                                   | dans le même esprit                         |
| switches                                 | [ˈswɪtʃ]                                    | change                                                                      | changement                                  |
| attack the problem from different angles | [əˈtæk ˈðə ˈprɒbləm ˈfrɒm ˈdɪfrənt ˈæŋɡəls] | try several solutions                                                       | attaquer le problème sous différents angles |
| underpin                                 | [ˌʌndərˈpɪn]                                | support                                                                     | étayer                                      |
| rewarding                                | [rɪˈwɔːrdɪŋ]                                | satisfying                                                                  | gratifiant                                  |
| astonishing                              | [əˈstɒnɪʃɪŋ]                                | amazing                                                                     | étonnant, stupéfiant                        |
| commit (to)                              | [kəˈmɪt]                                    | be dedicated to                                                             | s'engager (à)                               |
| pursue                                   | [pərˈsjuː]                                  | try to discover information                                                 | poursuivre                                  |
| trigger                                  | [ˈtrɪgər]                                   | cause                                                                       | déclencher, provoquer                       |
| fund                                     | [ˈfʌnd]                                     | provide money for                                                           | financer                                    |

## Analysis

|                               |                                                                                                                                                                                                              |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------ |
| Researchers                   | Professor Reuben Shaw, Salk Institute                                                                                                                                                                        |
| General topic                 |                                                                                                                                                                                                              |
| Published in                  | Science Daily, on 26 July 2019                                                                                                                                                                               |
| Procedure / what was examined | inactive gene LKB1 => cancer development + enzymes involved in inflammation / 12 potential enzymes that could suppress effect of LKB1 -> CRISPR + genetic analysis to inactivate each enzyme (+combinations) |
| Conclusion / discovery        | LKB1 <-> 2 enzymes (SIK1 and SIK3) that blocks tumor growth : SIK1 inactivated <-> increased tumor growth, SIK3 inactivated <-> tumor grows more aggressively => inflammation plays a role in lung cancer    |
| Remaining questions           | How do these kinase-driven changes in inflammation cause lung tumor growth ?                                                                                                                                 |

### 2019-12-01 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 01/12/2019

@@
   - name: Aurélie Pinchart
-date: 11-24-2019
+date: 12-01-2019
 preview: english.jpg
@@
 24/11/2019 : I watched a video about signal transduction pathways https://www.youtube.com/watch?v=236d5LDUFSs and I read the ninth chapter of "The Hobbit".
+
+25/11/2019 : I watched a video about electrochemical gradient https://www.youtube.com/watch?v=Ba02v7eoVWQ.
+
+27/11/2019 : I watched a video about viruses https://www.youtube.com/watch?v=8FqlTslU22s.
+
+29/11/2019 : I watched a video about organic molecules https://www.youtube.com/watch?v=tcmGGGJx9zI.
+
+01/12/2019 : I read the tenth chapter of "The Hobbit".

### 2019-12-08 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 08/12 + test % logo

@@
 01/12/2019 : I read the tenth chapter of "The Hobbit".
+
+03/12/2019 : I watched a video about microscopes https://www.youtube.com/watch?v=tVcEEw6qbBQ.
+
+05/12/2019 : I watched a video about reproductive adaptations https://www.youtube.com/watch?v=b_w4Nexv-0s.
+
+07/12/2019 : I watched a video about DNA replication https://www.youtube.com/watch?v=Qqe4thU-os8.
+
+08/12/2019 : I watched a video about imprinting https://www.youtube.com/watch?v=vwaiVxxpi7E and I read the eleventh chapter of "The Hobbit".

### 2019-12-14 _posts/2019-12-14-article-5/article-5.Rmd
article 5

---
title: "Article 5 : Possible new treatment strategy for lung cancer"
author:
  - name: Aurélie Pinchart
date: 12-14-2019
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Source of the article

H. Lee Moffitt Cancer Center & Research Institute. "Possible new treatment strategy for lung cancer: Combination therapy targeting KRAS mutation could provide benefit to nearly a third of lung cancer patients." ScienceDaily. ScienceDaily, 19 August 2019. <www.sciencedaily.com/releases/2019/08/190819140213.htm>.

Word count : 606

## Vocabulary

I used https://www.lexico.com/, https://dictionary.cambridge.org/ and https://www.wordreference.com/ to fill in this table.

| Vocabulary    | Pronunciation     | Definition / synonym                        | French translation           |
| ------------- | ----------------- | ------------------------------------------- | ---------------------------- |
| provide       | [prəˈvaɪd]        | give                                        | fournir                      |
| approach      | [əˈprəʊtʃ]        | the way of doing sth                        | approche                     |
| regulate      | [ˈrɛgjʊleɪt]      | control                                     | réguler                      |
| manner        | [ˈmænər]          | way, mode                                   | manière, façon               |
| occur         | [əˈk3ːr]          | happen                                      | se produire                  |
| melanoma      | [ˌmɛləˈnəʊmə]     | skin cancer                                 | mélanome                     |
| trametinib    | ?                 | cancer drug that inhibits MEK               | /                            |
| substantially | [səbˈstænʃəli]    | to a large extent                           | considérablement, énormément |
| dampen        | [ˈdæmpən]         | make feelings less strong (e.g. enthusiasm) | saper                        |
| sustain       | [səˈsteɪn]        | continue at the same level                  | soutenir, entreenir          |
| crucial       | [ˈkruːʃəl]        | very important                              | crucial                      |
| enhance       | [ɪnˈhɑːns]        | improve                                     | améliorer                    |
| viable        | [ˈvaɪəbəl]        | that can survive                            | viable                       |
| effectively   | [ɪˈfɛktɪvli]      | successfully                                | efficacement                 |
| conceptually  | [kənˈseptjʊəlɪ]   | based on abstract idea                      | conceptuellement             |
| novel         | [ˈnɒvəl]          | new                                         | nouveau, novateur            |
| oncogenic     | [ˌɒŋkə(ʊ)ˈdʒɛnɪk] | that causes the development of a tumor      | oncogénique                  |

## Analysis

|                               |                                                                                                                                                                                                                                                                                    |
| ----------------------------- | ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Amer A. Beg and Mengyu Xie (Moffitt Cancer Center )                                                                                                                                                                                                                                |
| General topic                 | mutations in the KRAS pathway <-> 30% lung cancers                                                                                                                                                                                                                                 |
| Published in                  | Science Daily, 19 August 2019                                                                                                                                                                                                                                                      |
| Procedure / what was examined | MEK kinase = possible target for treatment  : drug screens + cell line + animal model experiments => MEK inhibitor trametinib combinated to cytokines TNFα and IFNγ => more cell death than MEK inhibitor alone                                                                    |
| Conclusion / discovery        | MEK inhibitors increase the number of receptors for TNFα +IFNγ improves the anti-tumor activity of MEK inhibitors and TNFα +MEK inhibitors increase expression of TNFα and IFNγ target genes + PD-1 immune checkpoint inhibitor with MEK inhibitors => strongest tumor regression  |
| Remaining questions           | further studies : combining MEK inhibitors and other immune therapies that increase expression of TNFα and IFNγ => find out if  modulation of the immune microenvironment along with tumor signaling is a good strategy to cure lung cancer patients with KRAS mutations           |

### 2019-12-14 _posts/2019-12-14-article-5/article-5.Rmd
modif. article 5

@@
 date: 12-14-2019
+categories:
+  - KRAS
+  - MEK kinase
 output:

### 2019-12-15 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
(jusqu'au 8/12 + ancien logo)
chgt date M.E.A.L + énième tentative de mise en ligne % 8/12
jusqu'au 15/12 + mise en page

--- 2019-11-24 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
@@
   - name: Aurélie Pinchart
-date: 11-24-2019
+date: 12-15-2019
 preview: english.jpg
@@
 
-24/09/2019 : I read some articles for my presentation.
+# 2019
 
-25/09/2019 :I read some articles for my presentation.
+## September
 
-27/09/2019 :I read some articles for my presentation and I searched for some Youtube channels about science (especially Biology).
+* **24/09/2019** : I read some articles for my presentation.
+
+* **25/09/2019** :I read some articles for my presentation.
+
+* **27/09/2019** :I read some articles for my presentation and I searched for some Youtube channels about science (especially Biology).
 I found : iBiology, Biomentors Classes Online, Beverly Biology, Vincent Racaniello, Alex Lee, Sea&amp;me - Marine Biology stuff with Maria.
 
-29/09/2019 : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.
+* **29/09/2019** : I found other Youtube channels : Bleier Biology, Biology Bugbears, Bozeman science, Amoeba sisters, Free science lessons, Biomedical and Biological sciences.
 I read the first chapter of "The Hobbit".
 
-02/10/2019 : I read the wikipedia article about cockatiel for my Data Science homework.
+## October
 
-05/10/2019 : I read some articles for my presentation and I watched a video about diffusion (https://www.youtube.com/watch?v=jhszFBtBPoI).
+* **02/10/2019** : I read the wikipedia article about cockatiel for my Data Science homework.
 
-06/10/2019 : I read some articles for my presentation, I read the second chapter of "The Hobbit" and I watched a vide about cell cycle (https://www.youtube.com/watch?v=QVCjdNxJreE).
+* **05/10/2019** : I read some articles for my presentation and I watched a video about diffusion (https://www.youtube.com/watch?v=jhszFBtBPoI).
 
-09/10/2019 : I read an article for my presentation.
+* **06/10/2019** : I read some articles for my presentation, I read the second chapter of "The Hobbit" and I watched a vide about cell cycle (https://www.youtube.com/watch?v=QVCjdNxJreE).
 
-10/10/2019 : I watched a video about the respiratory system (https://www.youtube.com/watch?v=2guHOnEt0e8).
+* **09/10/2019** : I read an article for my presentation.
 
-11/10/2019 : I worked on my first article for my portfolio.
+* **10/10/2019** : I watched a video about the respiratory system (https://www.youtube.com/watch?v=2guHOnEt0e8).
 
-12/10/2019 : I read some articles for my presentation.
+* **11/10/2019** : I worked on my first article for my portfolio.
 
-13/10/2019 : I worked on my presentation and I read the third chapter of "The Hobbit".
+* **12/10/2019** : I read some articles for my presentation.
 
-14/10/2019 : I read some articles for my presentation.
+* **13/10/2019** : I worked on my presentation and I read the third chapter of "The Hobbit".
 
-15/10/2019 : I read some articles for my presentation and I watched a documentary about coral bleaching https://www.youtube.com/watch?v=5cr8S5tTiz4.
+* **14/10/2019** : I read some articles for my presentation.
 
-16/10/2019 : I read some articles for my presentation.
+* **15/10/2019** : I read some articles for my presentation and I watched a documentary about coral bleaching https://www.youtube.com/watch?v=5cr8S5tTiz4.
 
-17/10/2019 : I watched a video about the types of natural selection https://www.youtube.com/watch?v=DBPGLythma0.
+* **16/10/2019** : I read some articles for my presentation.
 
-19/10/2019 : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU. I also read the fouth chapter of "The Hobbit".
+* **17/10/2019** : I watched a video about the types of natural selection https://www.youtube.com/watch?v=DBPGLythma0.
 
-20/10/2019 : I watched a video about resting potential but it was said the opposite of what we were taught in class (so I don't put the link).
+* **19/10/2019** : I watched a video about marine biology https://www.youtube.com/watch?v=uWZXC3mjeZU. I also read the fouth chapter of "The Hobbit".
 
-22/10/2019 : I watched a video about predation https://www.youtube.com/watch?v=6jXwEOit5vM.
+* **20/10/2019** : I watched a video about resting potential but it was said the opposite of what we were taught in class (so I don't put the link).
 
-24/10/2019 : I watched a video about genetic drift https://www.youtube.com/watch?v=W0TM4LQmoZY and a video about natural selection https://www.youtube.com/watch?v=7VM9YxmULuo.
+* **22/10/2019** : I watched a video about predation https://www.youtube.com/watch?v=6jXwEOit5vM.
 
-26/10/2019 : I watched a video about the loss of biodiversity https://www.youtube.com/watch?v=vCkDxD0DV0Q and I read the fifth chapter of "T he Hobbit".
+* **24/10/2019** : I watched a video about genetic drift https://www.youtube.com/watch?v=W0TM4LQmoZY and a video about natural selection https://www.youtube.com/watch?v=7VM9YxmULuo.
 
-27/10/2019 : I watched a video about the protein structure and folding https://www.youtube.com/watch?v=hok2hyED9go.
+* **26/10/2019** : I watched a video about the loss of biodiversity https://www.youtube.com/watch?v=vCkDxD0DV0Q and I read the fifth chapter of "T he Hobbit".
 
-29/10/2019 : I watched a video about mutations https://www.youtube.com/watch?v=vl6Vlf2thvI.
+* **27/10/2019** : I watched a video about the protein structure and folding https://www.youtube.com/watch?v=hok2hyED9go.
 
-01/11/2019 : I watched a video about microscope drawings https://www.youtube.com/watch?v=NLKZ95aHqE4.
+* **29/10/2019** : I watched a video about mutations https://www.youtube.com/watch?v=vl6Vlf2thvI.
 
-02/11/2019 : I watched a video about ethology https://www.youtube.com/watch?v=BvLihzeQzGk.
+## November
 
-03/11/2019 : I watched a video about stress management https://www.youtube.com/watch?v=2vhIGYKW4gY and I read the sixth chapter of "The Hobbit".
+* **01/11/2019** : I watched a video about microscope drawings https://www.youtube.com/watch?v=NLKZ95aHqE4.
 
-05/11/2019 : I watched a video about ethology (the second part) https://www.youtube.com/watch?v=jEZIUVU0BCU.
+* **02/11/2019** : I watched a video about ethology https://www.youtube.com/watch?v=BvLihzeQzGk.
 
-07/11/2019 : I watched  the last part of the video about ethology https://www.youtube.com/watch?v=bspxe_-ilC4.
+* **03/11/2019** : I watched a video about stress management https://www.youtube.com/watch?v=2vhIGYKW4gY and I read the sixth chapter of "The Hobbit".
 
-09/11/2019 : I watched a video about enzymes https://www.youtube.com/watch?v=6Acx6b3Hzsk 
-10/11/2019 : I watched a video about germination https://www.youtube.com/watch?v=cmzhvl5kOc0 and I read the seventh chapter of "The Hobbit".
+* **05/11/2019** : I watched a video about ethology (the second part) https://www.youtube.com/watch?v=jEZIUVU0BCU.
 
-13/11/2019 : I watched a video about CRISPR https://www.youtube.com/watch?v=MnYppmstxIs.
+* **07/11/2019** : I watched  the last part of the video about ethology https://www.youtube.com/watch?v=bspxe_-ilC4.
 
-15/11/2019 : I watched a video about ATP https://www.youtube.com/watch?v=23ZzI6WZS28.
+* **09/11/2019** : I watched a video about enzymes https://www.youtube.com/watch?v=6Acx6b3Hzsk
 
-16/11/2019 : I watched a video about bacteria https://www.youtube.com/watch?v=ORB866QSGv8.
+* **10/11/2019** : I watched a video about germination https://www.youtube.com/watch?v=cmzhvl5kOc0 and I read the seventh chapter of "The Hobbit".
 
-17/11/2019 : I watched a video about autotrophs and heterotrophs https://www.youtube.com/watch?v=f8G7IulYxiA and I read the eighth of "The Hobbit".
+* **13/11/2019** : I watched a video about CRISPR https://www.youtube.com/watch?v=MnYppmstxIs.
 
-20/11/2019 : I watched a video about DNA and RNA https://www.youtube.com/watch?v=JQByjprj_mA.
+* **15/11/2019** : I watched a video about ATP https://www.youtube.com/watch?v=23ZzI6WZS28.
 
-21/11/2019 : I watched a video about skin https://www.youtube.com/watch?v=b9Fim9kKVLs.
+* **16/11/2019** : I watched a video about bacteria https://www.youtube.com/watch?v=ORB866QSGv8.
 
-23/11/2019 : I watched a video about reflex arc https://www.youtube.com/watch?v=SMcF01utk3Y.
+* **17/11/2019** : I watched a video about autotrophs and heterotrophs https://www.youtube.com/watch?v=f8G7IulYxiA and I read the eighth of "The Hobbit".
 
-24/11/2019 : I watched a video about signal transduction pathways https://www.youtube.com/watch?v=236d5LDUFSs and I read the ninth chapter of "The Hobbit".
+* **20/11/2019** : I watched a video about DNA and RNA https://www.youtube.com/watch?v=JQByjprj_mA.
+
+* **21/11/2019** : I watched a video about skin https://www.youtube.com/watch?v=b9Fim9kKVLs.
+
+* **23/11/2019** : I watched a video about reflex arc https://www.youtube.com/watch?v=SMcF01utk3Y.
+
+* **24/11/2019** : I watched a video about signal transduction pathways https://www.youtube.com/watch?v=236d5LDUFSs and I read the ninth chapter of "The Hobbit".
+
+* **25/11/2019** : I watched a video about electrochemical gradient https://www.youtube.com/watch?v=Ba02v7eoVWQ.
+
+* **27/11/2019** : I watched a video about viruses https://www.youtube.com/watch?v=8FqlTslU22s.
+
+* **29/11/2019** : I watched a video about organic molecules https://www.youtube.com/watch?v=tcmGGGJx9zI.
+
+## December
+
+* **01/12/2019** : I read the tenth chapter of "The Hobbit".
+
+* **03/12/2019** : I watched a video about microscopes https://www.youtube.com/watch?v=tVcEEw6qbBQ.
+
+* **05/12/2019** : I watched a video about reproductive adaptations https://www.youtube.com/watch?v=b_w4Nexv-0s.
+
+* **07/12/2019** : I watched a video about DNA replication https://www.youtube.com/watch?v=Qqe4thU-os8.
+
+* **08/12/2019** : I watched a video about imprinting https://www.youtube.com/watch?v=vwaiVxxpi7E and I read the eleventh chapter of "The Hobbit".
+
+* **10/12/2019** : I watched a video about protists and fungi https://www.youtube.com/watch?v=zK7Ckmxxqds.
+
+* **13/12/2019** : I went to the scientific workshop training and listened to the presentation of my friends.
+
+* **14/12/2019** : I watched a video about the heart https://www.youtube.com/watch?v=XpeeiqjRGB4.
+
+* **15/12/2019** : I watched a video about blood vessels https://www.youtube.com/watch?v=G2bJimNUjSI and i read the twelfth chapter of "The Hobbit".

### 2020-02-03 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 03/02/2020

@@
 * **15/12/2019** : I watched a video about blood vessels https://www.youtube.com/watch?v=G2bJimNUjSI and i read the twelfth chapter of "The Hobbit".
+
+* **17/12/2019** : I watched a video about study skills and habits https://www.youtube.com/watch?v=jCdTaLI5tVk.
+
+* **19/12/2019**  :I watched a video about Archaea https://www.youtube.com/watch?v=VGcT1-XaWgk.
+
+* **22/12/2019** : I read the 13th chapter of "The Hobbit".
+
+* **29/12/2019** : I read the 14th chapter of "The Hobbit".
+
+# 2020
+
+## January
+
+* **05/01/2020** : I read the 15th chapter of "The Hobbit".
+
+* **26/01/2020** : I read the 16th chapter of "The Hobbit".
+
+* **28/01/2020** : I read the 17th chapter of "The Hobbit".
+
+* **31/01/2020** : I read the 18th chapter of "The Hobbit".
+
+## February
+
+* **02/02/2020** : I read the last chapter of "The Hobbit".

### 2020-02-15 _posts/2020-02-14-article-6/article-6.Rmd
article 6 + jusqu'au 15/02/2020

---
title: "Article 6 : Protein decoy stymies lung cancer growth in mice"
author:
  - name: Aurélie Pinchart
date: 02-14-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Source of the article

Stanford Medicine. "Protein decoy stymies lung cancer growth in mice." ScienceDaily. ScienceDaily, 7 November 2019. <www.sciencedaily.com/releases/2019/11/191107160700.htm>

Word count : 930

## Vocabulary

I used https://www.lexico.com/, https://dictionary.cambridge.org/ and https://www.wordreference.com/ to fill in this table.

| Vocabulary        | Pronunciation         | Definition / synonym                         | French translation     |
| ----------------- | --------------------- | -------------------------------------------- | ---------------------- |
| decoy             | [ˈdiː.kɔɪ]            | sth. that diverts                            | leurre                 |
| stymie            | [ˈstaɪmi]             | block                                        | contrecarrer           |
| untreatable       | [ʌnˈtriːtəb(ə)l]      | that cannot be cured                         | incurable              |
| otherwise         | [ˈʌðərwaɪz]           | or esle                                      | sinon, autrement       |
| runaway           | [ˈrʌnəweɪ]            | out of control                               | hors de contrôle       |
| ligand            | [ˈlɪɡənd]             | molecule / ion attached on another molecule  | ligand                 |
| hook up           | [ˈhʊk ˈʌp]            | link                                         | s'attacher, s'associer |
| interfered        | [ˌɪntərˈfɪər]         | spoil / prevent the progress of a process    | interférer avec        |
| seek out          | [ˈsiːk ˈaʊt]          | search                                       | chercher               |
| thwart            | [ˈθwɔːrt]             | block                                        | contrecarrer           |
| interdisciplinary | [ˌɪntərˌdɪsɪˈplɪnəri] | multiple fields                              | interdisciplinaire     |
| squirting         | [ˈskw3ːrt]            | cause spurt of a liquid                      | asperger               |
| epithelial        | [ˌep.ɪˈθiː.li.əl]     | relating to epithelium                       | epithélial             |
| line              | [laɪn]                | cover                                        | recouvrir              |
| nested            | [nes′tid]             | one inside another                           | imbriqué, emboîté      |
| recruit           | [rɪˈkruːt]            | enroll                                       | recruter               |
| dampen            | ['dæmpən]             | make less strong / successful                | désenflammer           |
| unintentionally   | [ˌʌnɪnˈtɛnʃənəli]     | not deliberately                             | involontairement       |
| tightly           | [taɪtli]              | firmly                                       | fermement, solidement  |
| edge out          | [ɛdʒ ˈaʊt]            | displace, remove                             | évincer, déloger       |
| occur             | [əˈk3ːr]              | exist                                        | exister                |
| repel             | [rɪˈpɛl]              | keep away                                    | repousser              |
| painstaking       | ['peɪnzteɪkɪŋ]        | rigorous                                     | minutieux, rigoureux   |
| subtle            | ['sʌtəl]              | nearly undetectable                          | subtil                 |
| tweak             | [twiːk]               | slight change                                | petite modification    |
| propensity        | [prəʊˈpɛnsɪti]        | tendency                                     | propension, tendance   |
| ward off          | [ˈwɔːd ˈɒf]           | keep away                                    | repousser, éloigner    |
| instigate         | ['ɪnstɪgeɪt]          | cause                                        | être l'instigateur de  |
| prowess           | ['praʊəs/]            | great skill                                  | aptitude               |

## Analysis

|                               |                                                                                                                                                                                                         |
| ----------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Jennifer Cochran, Alejandro Sweet-Cordero, Jun Kim and Cesar Marquez (Stanford and UC-San Francisco)                                                                                                    |
| General topic                 | Creating a decoy protein to stop a chain reaction (leading to the spread of cancer)                                                                                                                     |
| Published in                  | Science Daily, 7 November 2019                                                                                                                                                                          |
| Procedure / what was examined | In 1 tpye of non-small cell lung cancer : mutation in KRAS gene -> CLCF1 binds to 3 receptors (+activation) and is released by fibroblasts (induction by cancerous epithelial cells) -> mechanism ?     |
| Conclusion / discovery        | CLCF1 first binds to CNTFR -> this complex attracts the other receptors (gp130 and LIFR) => more energy for the tumor -> making a decoy receptor similar to CNTFR (but inactive) -> tested on mice : OK |
| Remaining questions           | Will it work on humans ?                                                                                                                                                                                |

### 2020-02-29 _posts/2020-02-29-article-7/article-7.Rmd
article 7

---
title: "Article 7 : Newly developed nanoparticles help fight lung cancer in animal model"
author:
  - name: Aurélie Pinchart
date: 02-29-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Source of the article

Source : Wake Forest Baptist Medical Center. "Newly developed nanoparticles help fight lung cancer in animal model." ScienceDaily. ScienceDaily, 14 November 2019. <www.sciencedaily.com/releases/2019/11/191114115938.htm>.

Word count : 535

## Vocabulary
I used https://www.lexico.com/, https://dictionary.cambridge.org/, https://www.wordreference.com/, accentperfect.com/ to fill in this table

| Vocabulary        | Pronunciation       | Definition / synonym            | French translation          |
| ----------------- | ------------------- | ------------------------------- | --------------------------- |
| inhale            | [ɪnˈheɪl]           | breathe in                      | inspirer                    |
| metastatic        | [ˌmɛtəˈstætɪk]      | spreading                       | métastatique                |
| respond (to)      | [rɪˈspɒnd]          | react                           | réagir (à)                  |
| inhalable         | [ɪ’nheɪləbəl]       | that can be inhale              | inhalable                   |
| infiltrated       | [ˈɪnfɪltreɪt]       | move into sth.                  | s'infiltrer dans            |
| immunosuppressive | [ˌɪmjʊnəʊsəˈprɛsɪv] | drug that weakens immune system | immunosuppresseur           |
| novel             | [ˈnɒvəl]            | new, different                  | nouveau, novateur           |
| convert (to)      | [kənˈv3ːrt]         | change (to)                     | transformer, convertir (en) |
| deposit           | [dɪˈpɒzɪt]          | place                           | déposer                     |
| (lung) air sac    | [ˈeə ˌsæk]          | alveolus                        | alvéole pulmonaire          |
| systemic          | [sɪˈstɛmɪk]         | affecting all the body          | systémique, généralisé      |
| regression        | [rɪˈgrɛʃən]         | reverting to a previous state   | régression                  |
| prolong           | [prəʊˈlɒŋ]          | make longer                     | prolonger                   |
| eliminate         | [ɪˈlɪmɪneɪt]        | get rid of                      | éliminer, faire disparaître |
| robust            | [ˈrəʊbʌst]          | strong                          | robuste                     |
| deep-seated       | [ˌdiːpˈsiːtɪd]      | at a deep level                 | fermement ancré, profond    |
| feasibility       | [ˌfiːzəˈbɪlɪti]     | possibility of doing            | faisabilité                 |
| provisional       | [prəˈvɪʒənəl]       | temporary                       | provisoire                  |
| patent            | [ˈpeɪtənt]          | legal right                     | brevet                      |

## Analysis

|                               |                                                                                                                                                                                                                                                       |
| ----------------------------- | ----------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Dawen Zhao (Wake Forest School of Medicine)                                                                                                                                                                                                           |
| General topic                 | Inhalable nano-particles to treat lung cancer                                                                                                                                                                                                         |
| Published in                  | Science Daily, 14 November 2019                                                                                                                                                                                                                       |
| Procedure / what was examined | mice, inhalable particles (immunotherapy; non-invasive, access not only to the surface) -> taken up by APC cells => activation of immune response + radiation therapy; injection of immunomodulators not so efficient (<-> only surface of the tumor) |
| Conclusion / discovery        | regression of tumors + longer survival; elimination of tumors in some cases                                                                                                                                                                           |
| Remaining questions           | /                                                                                                                                                                                                                                                     |

### 2020-03-13 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
article 6 + jusqu'au 15/02/2020
article 8 + jusqu'au 13/03 + logo à gauche

@@
   - name: Aurélie Pinchart
-date: 12-15-2019
+date: 03-13-2020
 preview: english.jpg
@@
 * **02/02/2020** : I read the last chapter of "The Hobbit".
+
+* **08/02/2020** : I watched a video about plant structure https://www.youtube.com/watch?v=CNGn1qQCn4c.
+
+* **09/02/2020** : I watched a video about nitrogen cycle https://www.youtube.com/watch?v=jzrPiq3YuBM.
+
+## March
+
+* **07/03/2020** : I watched a video about plantibodies https://www.youtube.com/watch?v=gSLwVGHa6uM.
+
+* **09/03/2020** : I watched a video about hypotonic and hypertonic solutions https://www.youtube.com/watch?v=FU9xE8rxnOo.
+
+* **13/03/2020** : I watched a video about drug addiction and phsychoactive drugs https://www.youtube.com/watch?v=zhA1AB5yHmI.

### 2020-03-13 _posts/2020-03-13-article-8/article-8.Rmd
article 8 + jusqu'au 13/03 + logo à gauche

---
title: "Article 8 : Electronic nose can sniff out which lung cancer patients will respond to immunotherapy"
author:
  - name: Aurélie Pinchart
date: 03-13-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Source of the article

Source : European Society for Medical Oncology. "Electronic nose can sniff out which lung cancer patients will respond to immunotherapy." ScienceDaily. ScienceDaily, 17 September 2019. <www.sciencedaily.com/releases/2019/09/190917193627.htm>.
Word count : 960

## Vocabulary

I used https://www.lexico.com/, https://dictionary.cambridge.org/, https://www.wordreference.com/, https://www.revmed.ch/RMS/2008/RMS-152/Diagnostic-des-maladies-infectieuses-place-des-point-of-care-tests-POCT to fill in this table.

| Vocabulary          | Pronunciation          | Definition / synonym                                      | French translation     |
| ------------------- | ---------------------- | --------------------------------------------------------- | ---------------------- |
| gold standard       | [ˈɡəʊld ˈstændərd]     | reference                                                 | référence              |
| thoracic            | [θɔːˈræsɪk]            | relating to the thorax                                    | thoracique             |
| subset              | [ˈsʌbsɛt]              | set part of a larger one                                  | sous-ensemble          |
| biomarker           | [ˈbaɪ.əʊˌmɑː.kər]      | indicator                                                 | biomarqueur            |
| joint               | [ˈdʒɔɪnt]              | shared                                                    | conjoint               |
| hypothesize         | [haɪˈpɒθɪsaɪz]         | suppose                                                   | émettre une hypothèse  |
| exhale              | [ɛksˈheɪl]             | breathe out                                               | expirer                |
| device              | [dɪˈvaɪs]              | machine                                                   | appareil, dispositif   |
| sensor              | [ˈsɛnsər]              | electronic device that detects sth.                       | capteur, détecteur     |
| volatile            | [ˈvɒlətaɪl]            | that evaporates easily                                    | volatil                |
| indicate            | [ˈɪndɪkeɪt]            | point out                                                 | indiquer               |
| mixture             | [ˈmɪkstʃər]            | combinations of substances                                | mélange                |
| ambient             | [ˈæmbiənt]             | surrounding                                               | ambiant                |
| influence           | [ˈɪnfluəns]            | modify                                                    | influencer             |
| assess              | [əˈsɛs]                | evaluate                                                  | évaluer                |
| validate            | [ˈvælɪdeɪt]            | confirm, corroborate                                      | confirmer, valider     |
| distinguish         | [dɪˈstɪŋgwɪʃ]          | see difference between                                    | distinguer             |
| diagnostic          | [ˌdaɪəgˈnɒstɪk]        | used in diagnosis                                         | de diagnostic          |
| qualify             | [ˈkwɒlɪfaɪ]            | meet requirements                                         | remplir les conditions |
| point-of-care test  | [ˈpɔɪnt əv 'kɛə ˈtɛst] | diagnostic test that gives the results relatively quickly | ???                    |
| prospective         | [prəˈspɛktɪv]          | expected                                                  | futur                  |
| fatigue             | [fəˈtiːg]              | tiredness                                                 | fatigue                |
| bowel               | [ˈbaʊəl]               | intestine                                                 | intestin               |
| inflamed            | [ɪnˈfleɪmd]            | infected, swollen                                         | enflammé               |
| merely              | [ˈmɪərli]              | simply, only                                              | simplement, seulement  |
| scratch the surface | [ˈskrætʃ ˈðə ˈs3ːrfɪs] | deal with sth. superficially                              | effleurer le problème  |

## Analysis

|                               |                                                                                                                                                                                                                |
| ----------------------------- | -------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                   | Michel van den Heuvel (Radboud University Medical Centre), Rianne de Vries (Amsterdam University Medical Centres) and Mirte Muller (The Netherlands Cancer Institute)                                          |
| General topic                 | An electronic nose detecting if patients will respond to immunotherapy                                                                                                                                         |
| Published in                  | Science Daily, 17 September 2019                                                                                                                                                                               |
| Procedure / what was examined | way to replace immunohistochemistry (invasive + need time) -> analysis of breath (detection of volatile organic compounds); tested on 143 patients -> then treatment and verification with the standard method |
| Conclusion / discovery        | distinction between responders  and non-responders : 85% accuracy (=> avoid side effects of immunotherapy when non-responders)                                                                                 |
| Remaining questions           | /                                                                                                                                                                                                              |

### 2020-03-14 _posts/2019-09-18-article-1/article-1.Rmd
correction articles

@@
 Amyn Rojiani)                                                                                                                                                                                                                                                      |
-| Published in                | ScienceDaily, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
+| Published in                | Cancers, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
 | General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |

### 2020-03-14 _posts/2019-10-18-article-2/article-2.Rmd
correction articles

@@
 | General topic                 | the bad effect of antioxidants when you have lung caner                                                                                                                                                                                                                                                                                                                                                     |
-| Published in                  | Science News, 27 June 2019                                                                                                                                                                                                                                                                                                                                                                                  |
+| Published in                  | Cell, 27 June 2019                                                                                                                                                                                                                                                                                                                                                                                  |
 | Procedure / what was examined |  experiments on mice and humans  1) antioxidant- producing genes + effect of antioxidants 2) antioxidant // dietary supplement                                                                                                                                                                                                                                                                              |

### 2020-03-14 _posts/2019-11-02-article-3/article-3.Rmd
correction titre article 3
correction articles

@@
 
-## Soruce of the article
+## Source of the article
 
@@
 | General topic                 | detection of lung cancer                                                                                                                                                                        |
-| Published in                  | BBC, 10 September 2019 (presented a few days earlier in World Conference of Lung cancer in Barcelona)                                                                                           |
+| Published in                  | World Conference on Lung Cancer, 9 September 2019                                                                                            |
 | Procedure / what was examined | trial on more than 12,000 people who were at risk (smokers and former smokers, between 50 and 75 years old) : blood test + CT scans (= computed tomography scans) + detection of autoantibodies |

### 2020-03-14 _posts/2019-11-29-article-4/article-4.Rmd
modif. article 4 + test logo
correction articles

@@
 <www.sciencedaily.com/releases/2019/07/190726153155.htm>.
+
+Word count : 714
 
@@
 | Researchers                   | Professor Reuben Shaw, Salk Institute                                                                                                                                                                        |
-| General topic                 |                                                                                                                                                                                                              |
-| Published in                  | Science Daily, on 26 July 2019                                                                                                                                                                               |
+| General topic                 | Inactivating LKB1 triggers cancer development                                                                                                                                                                                                             |
+| Published in                  | Cancer Discovery, on 26 July 2019                                                                                                                                                                               |
 | Procedure / what was examined | inactive gene LKB1 => cancer development + enzymes involved in inflammation / 12 potential enzymes that could suppress effect of LKB1 -> CRISPR + genetic analysis to inactivate each enzyme (+combinations) |

### 2020-03-14 _posts/2020-02-14-article-6/article-6.Rmd
correction articles

@@
 | General topic                 | Creating a decoy protein to stop a chain reaction (leading to the spread of cancer)                                                                                                                     |
-| Published in                  | Science Daily, 7 November 2019                                                                                                                                                                          |
+| Published in                  | Nature Medicine, 7 November 2019                                                                                                                                                                          |
 | Procedure / what was examined | In 1 tpye of non-small cell lung cancer : mutation in KRAS gene -> CLCF1 binds to 3 receptors (+activation) and is released by fibroblasts (induction by cancerous epithelial cells) -> mechanism ?

### 2020-03-14 _posts/2020-02-29-article-7/article-7.Rmd
correction articles

@@
 | General topic                 | Inhalable nano-particles to treat lung cancer                                                                                                                                                                                                         |
-| Published in                  | Science Daily, 14 November 2019                                                                                                                                                                                                                       |
+| Published in                  | Nature Communications, 14 November 2019                                                                                                                                                                                                                       |
 | Procedure / what was examined | mice, inhalable particles (immunotherapy; non-invasive, access not only to the surface) -> taken up by APC cells => activation of immune response + radiation therapy; injection of immunomodulators not so efficient (<-> only surface of the tumor) |

### 2020-03-14 _posts/2020-03-13-article-8/article-8.Rmd
correction articles

@@
 | General topic                 | An electronic nose detecting if patients will respond to immunotherapy                                                                                                                                         |
-| Published in                  | Science Daily, 17 September 2019                                                                                                                                                                               |
+| Published in                  | Annals of Oncology, 17 September 2019                                                                                                                                                                               |
 | Procedure / what was examined | way to replace immunohistochemistry (invasive + need time) -> analysis of breath (detection of volatile organic compounds); tested on 143 patients -> then treatment and verification with the standard method |

### 2020-03-30 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 30/03

@@
   - name: Aurélie Pinchart
-date: 03-13-2020
+date: 03-30-2020
 preview: english.jpg
@@
 * **13/03/2020** : I watched a video about drug addiction and phsychoactive drugs https://www.youtube.com/watch?v=zhA1AB5yHmI.
+
+* **19/03/2020** : I watched a video about the immune system https://www.youtube.com/watch?v=fSEFXl2XQpc.
+
+* **21/03/2020** : I watched a video about the endocrine system (part 1) https://www.youtube.com/watch?v=-pJOnYvKC4U.
+
+* **27/03/2020** : I watched the second part of the video https://www.youtube.com/watch?v=LfqoRc68V5Q.
+
+* **28/03/2020** : I watched "The Lord Of The Rings : The Fellowship Of The Ring" (long version, of course).
+
+* **29/03/2020** : I watched "The Lord Of The Rings : The Two Tours".

### 2020-04-18 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
intro + CCL + bibilo + juqu'au 18/04

@@
 * **29/03/2020** : I watched "The Lord Of The Rings : The Two Tours".
+
+* **31/03/2020** : I wathed "The Lord Of The Rings : The Return Of The King".
+
+## Arpil
+
+* **05/04/2020** : I watched a video about Hardy & Weinberg equilibrum https://www.youtube.com/watch?v=7S4WMwesMts.
+
+* **18/04/2020** : I wathed e video about virus structure and reproduction https://www.youtube.com/watch?v=2--7fz9Fr_s.

### 2020-04-18 _posts/2020-04-18-bibliography/bibliography.Rmd
intro + CCL + bibilo + juqu'au 18/04

---
title: "Bibliography"
author:
  - name: Aurélie Pinchart
date: 04-18-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

* <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>, published on 23 September 2019 (consulted on 09/10/2019)

* Nicoletta Lanese. « Antioxidants may encourage the spread of lung cancer rather than prevent it ». Science News. June 27, 2019. https://www.sciencenews.org/article/antioxidants-lung-cancer-spread-prevent (consulted on30/10/2019)

* https://www.bbc.com/news/uk-scotland-49638208 published on 10 September 2019. (consulted on 13/11/2019)

* Salk Institute. “Two therapeutic targets identified for deadly lung cancer: Scientists discover a pair of enzymes that drive non-small-cell lung cancer by promoting inflammation.” ScienceDaily. ScienceDaily, 26 July 2019. <www.sciencedaily.com/releases/2019/07/190726153155.htm>. (consulted on 26/11/2019)

* H. Lee Moffitt Cancer Center & Research Institute. “Possible new treatment strategy for lung cancer: Combination therapy targeting KRAS mutation could provide benefit to nearly a third of lung cancer patients.” ScienceDaily. ScienceDaily, 19 August 2019. <www.sciencedaily.com/releases/2019/08/190819140213.htm>.  (consulted on 12/12/2019)

* Stanford Medicine. “Protein decoy stymies lung cancer growth in mice.” ScienceDaily. ScienceDaily, 7 November 2019. <www.sciencedaily.com/releases/2019/11/191107160700.htm>  (consulted on 11/02/2020)

* Wake Forest Baptist Medical Center. “Newly developed nanoparticles help fight lung cancer in animal model.” ScienceDaily. ScienceDaily, 14 November 2019. <www.sciencedaily.com/releases/2019/11/191114115938.htm>. (consulted on 25/02/2020)

* European Society for Medical Oncology. “Electronic nose can sniff out which lung cancer patients will respond to immunotherapy.” ScienceDaily. ScienceDaily, 17 September 2019. <www.sciencedaily.com/releases/2019/09/190917193627.htm>.  (consulted on 10/03/2020)

* https://www.wordreference.com/

* https://www.lexico.com/

* https://dictionary.cambridge.org

* https://en.wiktionary.org/

* https://www.revmed.ch/RMS/2008/RMS-152/Diagnostic-des-maladies-infectieuses-place-des-point-of-care-tests-POCT

* https://en.wikipedia.org/wiki/Lung_cancer (03/04/2020)

### 2020-04-18 _posts/2020-04-18-conclusion/conclusion.Rmd
intro + CCL + bibilo + juqu'au 18/04

---
title: "Conclusion"
author:
  - name: Aurélie Pinchart
date: 04-18-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I learnt that lung cancer is very complex because many proteins are involved in it and some of them work in a chain reaction. I also learnt that some researchers had developed a blood test to detect lung cancer earlier which is good as we often detect it too late. Some researchers are also developing an electronic nose to detect which patients will respond to immunotherapy and avoid the treatment (and potential side effects) to non-responders. I really also liked the idea of treating patients thanks to inhalable nanoparticles (and radiation therapy). I think it is a good idea as this method is non-invasive and patients are often weakened by the disease.

I thought that this work was very interesting because it made me learn a lot of new words and made me discover a new field of biology. I really enjoyed doing this work, even if it is sometimes hard to find the translation of some specific words.

### 2020-04-18 _posts/2020-04-18-introduction/introduction.Rmd
intro + CCL + bibilo + juqu'au 18/04

---
title: "Introduction"
author:
  - name: Aurélie Pinchart
date: 04-18-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

There are two main types of lung cancer: small-cell lung cancer and non-small-cell lung cancer. The symptoms are coughing, coughing up blood, weight loss, shortness of breath and chest pain. About 85% of lung cancers are due to tobacco smoking and the 15% left impact people who have never smoked and is due to genetic factors or pollution (such as second-hand smoke).

This disease can be diagnosed thanks to radiographs, computed tomography scan and biopsy. Lung cancer is a great cause of cancer related-death. 
My own grandfather died a few years ago because of it – he used to smoke a lot when I was a child, then he stopped but it seems I was too late… So I wanted to know a bit more about this disease. I especially wanted to know more about new discoveries in molecular and cellular biology to get an idea of how a lung cancer cell works and then also get an idea of future possible treatments. I also wanted to know if screening techniques had improved because waiting for many symptoms to diagnose lung cancer is sometimes too late to treat it properly.

In this portfolio, you will find 8 articles about recent researches mostly on non-small-cell lung cancer explaining how these cells work, what the possible future treatments are and how we can detect if you have lung cancer.

### 2020-04-26 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 26/04

@@
   - name: Aurélie Pinchart
-date: 03-30-2020
+date: 04-26-2020
 preview: english.jpg
@@
 * **18/04/2020** : I wathed e video about virus structure and reproduction https://www.youtube.com/watch?v=2--7fz9Fr_s.
+
+* **23/04/2020** :
+  + I watched a video about plant metabolism https://www.youtube.com/watch?v=XSig4PR_CXs&feature=share
+  + I watched a video about orchid's trap https://www.youtube.com/watch?v=_uHJGdTgtXE
+  + I watched a video about orchid wasp https://www.youtube.com/watch?v=0nfgibIYbg8
+  + I watched a video about nectar robbers https://www.youtube.com/watch?v=yBL_CIQD5aM
+
+* **24/04/2020** : I watched a video about cell signaling https://www.youtube.com/watch?v=-dbRterutHY.
+
+* **25/04/2020** : I watched a video about assumptions about marine biologists https://www.youtube.com/watch?v=hOE04I3TGL0.
+
+* **26/04/2020** : I watched a video about a turtle which have an exposed heart https://www.youtube.com/watch?v=c3s4n8MI2u4.
